Strength, mating success, and immune and dietary costs in a population sample of US women and men: a registered report

### 2024-09-13 paper.qmd
Added note to caption regarding posthoc results

```{r}
#| label: tbl-predictionsresults
#| tbl-cap: "Predictions. A plus sign (+) indicates a predicted significantly positive coefficient in all models of grip strength; a negative sign (-) indicates a predicted significantly negative coefficient in all such models; a zero (0) indicates a predicted non-significant coefficient in any such model; and a blank indicates not relevant. ✓: Supported in confirmatory study. ❌: Not supported in confirmatory study."

tribble(
              ~Outcome, ~Prediction, ~Result, ~Prediction, ~Result,
    "Partnered status",     "+",       "✓",       "-",       "✓",
   "Lifetime partners",     "+",       "✓",       "-",       "❌",
  "Past year partners",     "0",       "✓",       "0",       "✓",
    "Age at first sex",     "0",       "✓",       "0",       "✓",
            "Immunity",     "-",       "❌",      "0",       "✓",
              "Energy",     "0",       "❌",        "",        "",
             "Protein",     "+",       "✓",        "",        ""
  ) |>      
  tt() |> 
  style_tt(j=c(1,3), align = 'l') |> 
  group_tt(j = list("Strength coefficient" = 2:3, "Strength X sex coefficient" = 4:5))
```

>>>>

```{r}
#| label: tbl-predictionsresults
#| tbl-cap: "Predictions. A plus sign (+) indicates a predicted significantly positive coefficient in all models of grip strength; a negative sign (-) indicates a predicted significantly negative coefficient in all such models; a zero (0) indicates a predicted non-significant coefficient in any such model; and a blank indicates not relevant. ✓: Supported in confirmatory study. ❌: Not supported in confirmatory study. *The posthoc results found a significant negative association between lean mass and immunity, and a positive association with energy."

tribble(
              ~Outcome, ~Prediction, ~Result, ~Prediction, ~Result,
    "Partnered status",     "+",       "✓",       "-",       "✓",
   "Lifetime partners",     "+",       "✓",       "-",       "❌",
  "Past year partners",     "0",       "✓",       "0",       "✓",
    "Age at first sex",     "0",       "✓",       "0",       "✓",
            "Immunity",     "-",       "❌*",      "0",       "✓",
              "Energy",     "0",       "❌*",        "",        "",
             "Protein",     "+",       "✓",        "",        ""
  ) |>      
  tt() |> 
  style_tt(j=c(1,3), align = 'l') |> 
  group_tt(j = list("Strength coefficient" = 2:3, "Strength X sex coefficient" = 4:5))
```
